---
title: "Homework 6"
output: html_notebook
---

__Question 1:__ Choose a country (not the US). 

Use the package maps to show a map of the country:

```{r}
library(maps)
library(mapdata)
map("worldHires","South Korea",col="gray90",fill=TRUE)
```

The dataset `world.cities` included in the map package contain information about the location and population of several cities in the world. Create a new data frame containing only the cities in the country you chose:

```{r}
cities2=world.cities
cities3=subset(cities2, country.etc == "Korea South")
```

Now take a look the cities, choose a population threshold that will lead to only about 20 cities in your dataset and plot the location of these cities in the country map using the `map.cities` function :

```{r}
cities4=subset(cities3,pop>380000)
map("world","Korea South")
map.cities(x=world.cities,country="Korea South",  minpop=380000, label=TRUE)

```

Now instead of using `map.cities`, create a new dataframe `myCities` with only the latitude and longitude of the cities you chose above. You are going to need to get this information directly from the `world.cities` dataset.

```{r}
myCities=cities4[,c("long","lat")]

```

Use the geosphere package to calculate the distances between each pair of cities (use the `distm` function). You will need to add row and column names to the result of `distm`.

```{r}
library(geosphere)
dre=distm(myCities)
rownames(dre)=cities4[,"name"]
mdis = as.dist(dre)/10000

```

Use this data frame to perform a PCoA, plot the results and compare to your original graph of the cities.

```{r}
library(plotly)
library(ape)
pcoaRes3 <- pcoa(mdis,correction="lingoes")
pcoaResDf3 <- data.frame(pcoaRes3$vectors)
p = plot_ly(pcoaResDf3, x = ~Axis.1 , y = ~Axis.2, text = rownames(dre), type = 'scatter',
             mode = "markers", marker = list(size = 11)) 
 
p <- layout(p, title = "PCoA from South Korean City Distances", 
       xaxis = list(title = "PC 1"),
       yaxis = list(title = "PC 2"))
p
```






```
